### 2022-06-01 avs/datovy_paralelismus/datovy_paralelismus.tex
Update datovy paralelismus

\begin{compactitem}
    \item Flynnova taxonomie: \begin{compactitem}
        \item Single instruction stream, single data stream (SISD)
        \item Single instruction stream, multiple data streams (SIMD)
        \item Multiple instruction streams, single data stream (MISD)
        \item Multiple instruction streams, multiple data streams (MIMD)
    \end{compactitem}

>>>>

\begin{compactitem}
    \item Flynnova taxonomie: \begin{compactitem}
        \item SISD (\textit{single instruction stream, single data stream} -- Skalární procesor.
        \item SIMD (\textit{single instruction stream, multiple data streams} -- Vektorové procesory.
        \item MISD (\textit{multiple instruction streams, single data stream} -- Používá se pouze ve velmi speciálních případech.
        \item MIMD (\textit{multiple instruction streams, multiple data streams} -- Vícevláknové procesory.
    \end{compactitem}
